### 2025-02-09 data-visualization.qmd
20250209 - density plot with histogram
20250209 - use coord_cartesian to zoom in plot w/o removing data

@@

ggplot2::ggplot(
  data = player_stats_seasonal %>% 
    filter(position_group %in% c("QB","RB","WR","TE")),
  aes(
    x = age,
    y = fantasyPoints)) +
  geom_point() +
  geom_smooth() +
  scale_x_continuous(
    expand = c(0,0)
  ) +
  scale_y_continuous(
    expand = c(0,0),
    lim = c(0,NA)
  ) +
  labs(
    x = "Player's Age (years)",
    y = "Fantasy Points (Season)",
    title = "Fantasy Points (Season) by Player Age"
  ) +
  theme_bw() +
  facet_wrap(vars(position_group)) # facet by position_group
```

>>>>

```{r}
#| label: fig-histogramDensity
#| fig-cap: "Density Plot with Histogram and Rug Plot."
#| fig-alt: "Density Plot with Histogram and Rug Plot."

@@

ggplot2::ggplot(
  data = player_stats_seasonal %>% 
    filter(position_group %in% c("QB","RB","WR","TE")),
  aes(
    x = age,
    y = fantasyPoints)) +
  geom_point() +
  geom_smooth() +
  coord_cartesian(
    ylim = c(0,NA), # set limits of y-axis
    expand = FALSE) + # don't add space between axes and data
  labs(
    x = "Player's Age (years)",
    y = "Fantasy Points (Season)",
    title = "Fantasy Points (Season) by Player Age"
  ) +
  theme_bw() +
  facet_wrap(vars(position_group)) # facet by position_group
```
